The regularity of ODEs and thimble integrals \\ with respect to Borel summation

### 2025-11-04 SIGMA/SIGMA_submission/borel_reg_submission.tex
Finalize third-round revisions

From the expression above, we can see that $v_1$ has only two singularities in the complex plane: one at $\zeta_1 = 0$ from the factor of $\zeta_1^{-1/2}$, and one at $\zeta_1 = -2$ from the hypergeometric function. Therefore, $v_1$ is holomorphic throughout the sector $\Omega_1 = \C \smallsetminus \mathcal{J}^\pi_{\zeta_1, 0}$. Since $v_1$ has a power law singularity at $\infty$, it is uniformly of exponential type $\Lambda$ for any $\Lambda > 0$. Therefore, it belongs to the space $\singexp{-1/2}{\Lambda}(\Omega_1)$ for all $\Lambda > 0$. By thinking about its shifted Taylor expansion around $\zeta_1 = 0$, we can see more precisely that $v_1$ belongs to
\[ -i\sqrt{2}\,\zeta_1^{-1/2} + \singexp{1/2}{\Lambda}(\Omega_1) \]
for all $\Lambda > 0$. As discussed in Section~\ref{big-idea}, we conclude that $v_1$ has a well-defined Laplace transform along any ray from $\zeta = 1$ except the one going directly left. Its Laplace transform can be written as
\[ \laplace^\theta_{\zeta, 1} v_1 = e^{-z} z^{-1/2}\,W_1\,, \]
where $W_1$ is a holomorphic function on the slit plane $z \notin (-\infty, 0]$ which is bounded outside any constant-radius neighborhood of the ray $z \in (-\infty, 0]$.
%
\subsubsection{Focus on $\zeta = -1$}\label{neg-root-AL}
%
Let us find a germ in $(\zeta+1)^{\tau_{-1}-1}\,\mathcal{O}_{\zeta=-1}$, for some $\tau_{-1} \in (0, 1)$, that satisfies equation~\eqref{diff-eq:spatial-mod-bessel-AL}. In the rescaled coordinate from Section~\ref{pos-root-AL}, this is the point $\xi_1 = 1$. Looking again through Kummer's table of solutions, we find another expression \cite[formula~15.10.14]{dlmf} that represents a germ in $(1-\xi_1)^{-1/2}\,\mathcal{O}_{\xi_1=1}$:
\begin{alignat*}{2}
v_{-1} &=\;& (1-\xi_1)^{-1/2} &\;{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; 1-\xi_1\big) \\[1mm]
&=\;& \sqrt{2}\,\zeta_{-1}^{-1/2} &\;{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big),
\,\end{alignat*}
where $\zeta_{-1}$ is the coordinate with $\zeta = -1 + \zeta_{-1}$. By the same reasoning as before, $v_{-1}$ is holomorphic throughout the sector $\Omega_{-1} = \C \smallsetminus \mathcal{J}^0_{\zeta_{-1}, 0}$, and it belongs to the space
\[ \sqrt{2}\,\zeta_{-1}^{-1/2} + \singexp{1/2}{\Lambda}(\Omega_1) \]
for all $\Lambda > 0$. It has a well-defined Laplace transform along any ray from $\zeta = -1$ except the one going directly right, and its Laplace transform can be written as
\[ \laplace^\theta_{\zeta, -1} v_1 = e^z z^{-1/2}\,W_{-1}, \]
where $W_{-1}$ is a holomorphic function on the slit plane $z \notin [0, \infty)$ which is bounded outside any constant-radius neighborhood of the ray $z \in [0, \infty)$.

@@

As we did with the Airy--Lucas functions, we will use the substitution $t = 2uy^{1/2}$ to rewrite the generalized Airy function $\mathrm{A}_1(y,p)$ in terms of a thimble integral. We get
\[ \mathrm{A}_1(y,p) = (12 z)^{(1-p)/3}\,I_+\big(\tfrac{2}{3}y^{3/2},p\big) \]
with
\[ I_+(z,p) = \frac{1}{2\pi i} \int_{\mathcal{C}^\theta_1} \exp\left[-z\left(4u^3 - 3u\right)\right]\,\frac{du}{u^p}\,. \]
To find the right contour $\mathcal{C}_1^\theta$, we first note that the mapping $\zeta = 4u^3 - 3u$ is familiar, up to a sign, from Section~\ref{sec:airy}. In particular, we already know its critical points $u = \pm\tfrac{1}{2}$ and the corresponding critical values $\zeta = \pm 1$. To get the desired integral, $\mathcal{C}_1^\theta$ should be the thimble through $u = -\tfrac{1}{2}$ over the ray $\mathcal{J}^\theta_1$. However, this thimble does not live on the complex plane, like it did for the classical Airy function. When $p$ is a positive integer, the volume form $du/u^p$ has a pole at $u = 0$, so we put $\mathcal{C}_1^\theta$ as a contour on $\C^\times$. More generally, for any complex value of $p$, we can put $\mathcal{C}_1^\theta$ on the universal cover $\widetilde{\C^\times}$.
%
We will now show, in the case $p = 1$, that equation~\eqref{eqn:I} has a frame of Borel regular solutions---as long as the constant solution $\mathrm{B}_0(z, 1)$ counts as Borel regular. For $\mathrm{A}_1(y, p)$ to satisfy the generalized Airy equation, $I_+(z,1)$ must satisfy the equation
\begin{equation}\label{eqn:I}
\left[\big[\big(\tfrac{\partial}{\partial z}\big)^2 - 1\big] + z^{-1} \left(\tfrac{\partial}{\partial z}\right)^2 - \tfrac{1}{9} z^{-2} \right] \tfrac{\partial}{\partial z} \Phi = 0\,.
\end{equation}
Equivalently, $\tfrac{\partial}{\partial z} I_+(z, 1)$ satisfies the modified Bessel equation \eqref{eqn:reg-mod-bessel-AL} with parameter $1/3$. We can now follow the reasoning of Section~\ref{big-idea}, viewing that frequency domain differential equation~\eqref{eqn:I} as the image under $\laplace_{\zeta, \alpha}$ of the position domain integral equation
\begin{equation}\label{int-eq:position-I}
\left[ \big[ \zeta^2 - 1 \big] - \fracderiv{-1}{\zeta}{\alpha} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \fracderiv{-2}{\zeta}{\alpha} \right] (-\zeta)\,v^{(1)} = 0\,.
\end{equation}
In Sections \ref{pos-root-AL} and \ref{neg-root-AL}, we found solutions $v_{\pm 1}$ of the closely related equation~\eqref{int-eq:spatial-mod-bessel-AL}, which we can turn into solutions $v^{(1)}_{\pm 1} = \zeta^{-1} v_{\pm 1}$ of equation~\eqref{int-eq:position-I}.

@@

\[ I(z) = \frac{\sqrt{3}}{irp} e^{-qa_3z} K_{1/3}\left(\frac{a_3 z}{r}\right) \]

@@

\[ \tfrac{\partial}{\partial \zeta} \sqrt{\zeta^4 - \omega^2} = \frac{2\zeta^3}{\sqrt{\zeta^4 - \omega^2}}, \]

@@

\[ \int_{\mathcal{C}_1^\theta(\zeta)} du = \frac{2i}{\sqrt{3}} \left(-\frac{1}{2} + \frac{\zeta}{2}\right)^{1/2}\;{}_2 F_1\left(\frac{1}{6}, \frac{5}{6}; \frac{3}{2}; \frac{1}{2} - \frac{\zeta}{2}\right)\,, \]

@@

To do this, first notice that if $\eta$ and $y$ are conjugate variables under Borel transform, meaning 
\begin{equation*}\begin{split}
\sum_{n\geq 0}a_n\eta^{-n-1}  \overset{\borel}{\longrightarrow} \sum_{n\geq 0}\frac{a_n}{n!} y^{n} 
\end{split}\end{equation*} 
then $t=\frac{3}{2}yx^{-3/2}$ is the conjugate variable of $q=\frac{2}{3}\eta x^{3/2}$ up to correction by a factor of $\frac{3}{2}x^{-3/2}$
\begin{equation*}\begin{split}
\sum_{n\geq 0}a_nq^{-n-1}=\sum_{n\geq 0}a_nx^{-3/2(n+1)}\left(\frac{2}{3}\eta\right)^{-n-1}  \overset{\borel}{\longrightarrow} \sum_{n\geq 0}\frac{a_nx^{-3/2(n+1)}}{n!}\left(\frac{3}{2}\right)^{n+1}  y^{n}=\frac{3}{2}x^{-3/2}\sum_{n\geq 0}\frac{a_n}{n!} t^{n}\,. 
\end{split}\end{equation*}
In addition, $\psi_{B,\pm}(x,y)=\frac{1}{x}\phi_{\pm}(t)$, therefore we expect that $\psi(x,\eta)=x^{1/2}\Phi(q)$. Assume that $\psi(x,y)$ is a solution of \eqref{WKB_Airy}, then $\Phi(q)$ satisfies
\begin{equation}
\label{eq_Phi}
\left[\left(\frac{d}{dx}\right)^2+x^{-1}\frac{d}{dx}-\frac{1}{4}x^{-2} - \eta^2 x \right] \Phi(q) = 0
\end{equation}

\begin{proof}
\begin{equation*}\begin{split}
&\left[\big(\tfrac{d}{dx}\big)^2 - \eta^2 x \right] \psi(x, \eta) = 0\\
&\left[\big(\tfrac{d}{dx}\big)^2 - \eta^2 x \right] x^{1/2}\Phi(q) = 0\\
&\frac{d}{dx}\left[\tfrac{1}{2}x^{-1/2}\Phi+x^{1/2}\tfrac{d}{dx}\Phi\right]-\eta^2x^{3/2}\Phi=0\\
&-\tfrac{1}{4}x^{-3/2}\Phi+\tfrac{1}{2}x^{-1/2}\tfrac{d}{dx}\Phi+\tfrac{1}{2}x^{-1/2}\tfrac{d}{dx}\Phi+x^{1/2}\left(\tfrac{d}{dx}\right)^2\Phi-\eta^2x^{3/2}\Phi=0\\
&\left[x^{1/2}\big(\tfrac{d}{dx}\big)^2+x^{-1/2}\tfrac{d}{dx}-\tfrac{1}{4}x^{-3/2}-\eta^2x^{3/2}\right]\Phi=0\\
&\left[\big(\tfrac{d}{dx}\big)^2+x^{-1}\tfrac{d}{dx}-\tfrac{1}{4}x^{-2}-\eta^2x\right]\Phi=0
\end{split}\end{equation*}
\end{proof}
Now, rewrite \eqref{eq_Phi} in the coordinates $q=\frac{2}{3}\eta x^{3/2}$: 
\begin{equation*}\begin{split}
&\left[\big(\tfrac{d}{dx}\big)^2+x^{-1}\tfrac{d}{dx}-\tfrac{1}{4}x^{-2}-\eta^2x\right]\Phi=0\\
&\left[\eta^2x\big(\tfrac{d}{dq}\big)^2+\frac{1}{2}\eta x^{-1/2}\tfrac{d}{dq}+x^{-1}\cdot\, \eta\,  x^{1/2}\tfrac{d}{dq}-\tfrac{1}{4}x^{-2}-\eta^2x\right]\Phi=0\\
&\left[\eta^2x\big(\tfrac{d}{dq}\big)^2+\tfrac{3}{2}\eta x^{-1/2}\tfrac{d}{dq}-\tfrac{1}{4}x^{-2}-\eta^2x\right]\Phi=0\\
&\left[\big(\tfrac{d}{dq}\big)^2+\tfrac{3}{2}\eta^{-1} x^{-3/2}\tfrac{d}{dq}-\tfrac{1}{4}\eta^{-2}x^{-3}-1\right]\Phi=0\\
&\left[\big(\tfrac{d}{dq}\big)^2+q^{-1}\tfrac{d}{dq}-\tfrac{1}{9}q^{-2}-1\right]\Phi=0\,.
\end{split}\end{equation*}
This shows that $\Phi(q)$ satisfies the transformed Airy equation \eqref{eqn:reg-mod-bessel}.

>>>>

From the expression above, we can see that $v_1$ has only two singularities in the complex plane: one at $\zeta_1 = 0$ from the factor of $\zeta_1^{-1/2}$, and one at $\zeta_1 = -2$ from the hypergeometric function. Therefore, $v_1$ is holomorphic throughout the sector $\Omega_1 = \C \smallsetminus \mathcal{J}^\pi_{\zeta_1, 0}$. Since $v_1$ has a power law singularity at $\infty$, it is uniformly of exponential type $\Lambda$ for any $\Lambda > 0$. Therefore, it belongs to the space $\singexp{-1/2}{\Lambda}(\Omega_1)$ for all $\Lambda > 0$. By thinking about its shifted Taylor expansion around $\zeta_1 = 0$, we can see more precisely that $v_1$ belongs to
\[ -i\sqrt{2}\,\zeta_1^{-1/2} + \singexp{1/2}{\Lambda}(\Omega_1) \]
for all $\Lambda > 0$. As discussed in Section~\ref{big-idea}, we conclude that $v_1$ has a well-defined Laplace transform along any ray from $\zeta = 1$ except the one going directly left. Its Laplace transform can be written as
\[ \laplace^\theta_{\zeta, 1} v_1 = e^{-z} z^{-1/2}\,W_1\,, \]
where $W_1$ is a holomorphic function on the slit plane $z \notin (-\infty, 0]$ which is bounded outside any constant-radius neighborhood of the ray $z \in (-\infty, 0]$.
%
\subsubsection{Focus on $\zeta = -1$}\label{neg-root-AL}
%
Let us find a germ in $(\zeta+1)^{\tau_{-1}-1}\,\mathcal{O}_{\zeta=-1}$, for some $\tau_{-1} \in (0, 1)$, that satisfies equation~\eqref{diff-eq:spatial-mod-bessel-AL}. In the rescaled coordinate from Section~\ref{pos-root-AL}, this is the point $\xi_1 = 1$. Looking again through Kummer's table of solutions, we find another expression \cite[formula~15.10.14]{dlmf} that represents a germ in $(1-\xi_1)^{-1/2}\,\mathcal{O}_{\xi_1=1}$:
\begin{alignat*}{2}
v_{-1} &=\;& (1-\xi_1)^{-1/2} &\;{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; 1-\xi_1\big) \\[1mm]
&=\;& \sqrt{2}\,\zeta_{-1}^{-1/2} &\;{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big)\,,
\end{alignat*}
where $\zeta_{-1}$ is the coordinate with $\zeta = -1 + \zeta_{-1}$. By the same reasoning as before, $v_{-1}$ is holomorphic throughout the sector $\Omega_{-1} = \C \smallsetminus \mathcal{J}^0_{\zeta_{-1}, 0}$, and it belongs to the space
\[ \sqrt{2}\,\zeta_{-1}^{-1/2} + \singexp{1/2}{\Lambda}(\Omega_1) \]
for all $\Lambda > 0$. It has a well-defined Laplace transform along any ray from $\zeta = -1$ except the one going directly right, and its Laplace transform can be written as
\[ \laplace^\theta_{\zeta, -1} v_1 = e^z z^{-1/2}\,W_{-1}\,, \]
where $W_{-1}$ is a holomorphic function on the slit plane $z \notin [0, \infty)$ which is bounded outside any constant-radius neighborhood of the ray $z \in [0, \infty)$.

@@

As we did with the Airy--Lucas functions, we will use the substitution $t = 2uy^{1/2}$ to rewrite the generalized Airy function $\mathrm{A}_1(y,p)$ in terms of a thimble integral. We get
\[ \mathrm{A}_1(y,p) = (12 z)^{(1-p)/3}\,I_+\big(\tfrac{2}{3}y^{3/2},p\big) \]
with
\[ I_+(z,p) = \frac{1}{2\pi i} \int_{\mathcal{C}^\theta_1} \exp\left[-z\left(4u^3 - 3u\right)\right]\,\frac{du}{u^p}\,. \]
To find the right contour $\mathcal{C}_1^\theta$, we first note that the mapping $\zeta = 4u^3 - 3u$ is familiar, up to a sign, from Section~\ref{sec:airy}. In particular, we already know its critical points $u = \pm\tfrac{1}{2}$ and the corresponding critical values $\zeta = \pm 1$. To get the desired integral, $\mathcal{C}_1^\theta$ should be the thimble through $u = -\tfrac{1}{2}$ over the ray $\mathcal{J}^\theta_1$. However, this thimble does not live on the complex plane, like it did for the classical Airy function. When $p$ is a positive integer, the volume form $du/u^p$ has a pole at $u = 0$, so we put $\mathcal{C}_1^\theta$ as a contour on $\C^\times$. More generally, for any complex value of $p$, we can put $\mathcal{C}_1^\theta$ on the universal cover $\widetilde{\C^\times}$. We will now show, in the case $p = 1$, that equation~\eqref{eqn:I} has a frame of Borel regular solutions---as long as the constant solution $\mathrm{B}_0(z, 1)$ counts as Borel regular. For $\mathrm{A}_1(y, p)$ to satisfy the generalized Airy equation, $I_+(z,1)$ must satisfy the equation
\begin{equation}\label{eqn:I}
\left[\big[\big(\tfrac{\partial}{\partial z}\big)^2 - 1\big] + z^{-1} \left(\tfrac{\partial}{\partial z}\right)^2 - \tfrac{1}{9} z^{-2} \right] \tfrac{\partial}{\partial z} \Phi = 0\,.
\end{equation}
Equivalently, $\tfrac{\partial}{\partial z} I_+(z, 1)$ satisfies the modified Bessel equation \eqref{eqn:reg-mod-bessel-AL} with parameter $1/3$. We can now follow the reasoning of Section~\ref{big-idea}, viewing that frequency domain differential equation~\eqref{eqn:I} as the image under $\laplace_{\zeta, \alpha}$ of the position domain integral equation
\begin{equation}\label{int-eq:position-I}
\left[ \big[ \zeta^2 - 1 \big] - \fracderiv{-1}{\zeta}{\alpha} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \fracderiv{-2}{\zeta}{\alpha} \right] (-\zeta)\,v^{(1)} = 0\,.
\end{equation}
In Sections \ref{pos-root-AL} and \ref{neg-root-AL}, we found solutions $v_{\pm 1}$ of the closely related equation~\eqref{int-eq:spatial-mod-bessel-AL}, which we can turn into solutions $v^{(1)}_{\pm 1} = \zeta^{-1} v_{\pm 1}$ of equation~\eqref{int-eq:position-I}.

@@

\[ I(z) = \frac{\sqrt{3}}{irp} e^{-qa_3z} K_{1/3}\left(\frac{a_3 z}{r}\right)\,. \]

@@

\[ \tfrac{\partial}{\partial \zeta} \sqrt{\zeta^4 - \omega^2} = \frac{2\zeta^3}{\sqrt{\zeta^4 - \omega^2}}\,, \]

@@

\[ \int_{\mathcal{C}_1^\theta(\zeta)} du = \frac{2i}{\sqrt{3}} \left(-\frac{1}{2} + \frac{\zeta}{2}\right)^{1/2}\;{}_2 F_1\left(\frac{1}{6}, \frac{5}{6}; \frac{3}{2}; \frac{1}{2} - \frac{\zeta}{2}\right)\,. \]

@@

To do this, first notice that if $\eta$ and $y$ are conjugate variables under Borel transform, meaning 
\begin{equation*}\begin{split}
\sum_{n\geq 0}a_n\eta^{-n-1}  \overset{\borel}{\longrightarrow} \sum_{n\geq 0}\frac{a_n}{n!} y^{n} 
\end{split}\end{equation*} 
then $t=\frac{3}{2}yx^{-3/2}$ is the conjugate variable of $q=\frac{2}{3}\eta x^{3/2}$ up to correction by a factor of $\frac{3}{2}x^{-3/2}$
\begin{equation*}\begin{split}
\sum_{n\geq 0}a_nq^{-n-1}=\sum_{n\geq 0}a_nx^{-3/2(n+1)}\left(\frac{2}{3}\eta\right)^{-n-1}  \overset{\borel}{\longrightarrow} \sum_{n\geq 0}\frac{a_nx^{-3/2(n+1)}}{n!}\left(\frac{3}{2}\right)^{n+1}  y^{n}=\frac{3}{2}x^{-3/2}\sum_{n\geq 0}\frac{a_n}{n!} t^{n}\,. 
\end{split}\end{equation*}
In addition, $\psi_{B,\pm}(x,y)=\frac{1}{x}\phi_{\pm}(t)$, therefore we expect that $\psi(x,\eta)=x^{1/2}\Phi(q)$. Assume that $\psi(x,y)$ is a solution of \eqref{WKB_Airy}. Then $\Phi(q)$ satisfies
\begin{equation}
\label{eq_Phi}
\left[\left(\frac{d}{dx}\right)^2+x^{-1}\frac{d}{dx}-\frac{1}{4}x^{-2} - \eta^2 x \right] \Phi(q) = 0\,,
\end{equation}
because
\begin{equation*}\begin{split}
&\left[\big(\tfrac{d}{dx}\big)^2 - \eta^2 x \right] \psi(x, \eta) = 0\\
&\left[\big(\tfrac{d}{dx}\big)^2 - \eta^2 x \right] x^{1/2}\Phi(q) = 0\\
&\frac{d}{dx}\left[\tfrac{1}{2}x^{-1/2}\Phi+x^{1/2}\tfrac{d}{dx}\Phi\right]-\eta^2x^{3/2}\Phi=0\\
&-\tfrac{1}{4}x^{-3/2}\Phi+\tfrac{1}{2}x^{-1/2}\tfrac{d}{dx}\Phi+\tfrac{1}{2}x^{-1/2}\tfrac{d}{dx}\Phi+x^{1/2}\left(\tfrac{d}{dx}\right)^2\Phi-\eta^2x^{3/2}\Phi=0\\
&\left[x^{1/2}\big(\tfrac{d}{dx}\big)^2+x^{-1/2}\tfrac{d}{dx}-\tfrac{1}{4}x^{-3/2}-\eta^2x^{3/2}\right]\Phi=0\\
&\left[\big(\tfrac{d}{dx}\big)^2+x^{-1}\tfrac{d}{dx}-\tfrac{1}{4}x^{-2}-\eta^2x\right]\Phi=0\,.
\end{split}\end{equation*}
%
Now, rewrite \eqref{eq_Phi} in the coordinates $q=\frac{2}{3}\eta x^{3/2}$: 
\begin{equation*}\begin{split}
&\left[\big(\tfrac{d}{dx}\big)^2+x^{-1}\tfrac{d}{dx}-\tfrac{1}{4}x^{-2}-\eta^2x\right]\Phi=0\\
&\left[\eta^2x\big(\tfrac{d}{dq}\big)^2+\frac{1}{2}\eta x^{-1/2}\tfrac{d}{dq}+x^{-1}\cdot\, \eta\,  x^{1/2}\tfrac{d}{dq}-\tfrac{1}{4}x^{-2}-\eta^2x\right]\Phi=0\\
&\left[\eta^2x\big(\tfrac{d}{dq}\big)^2+\tfrac{3}{2}\eta x^{-1/2}\tfrac{d}{dq}-\tfrac{1}{4}x^{-2}-\eta^2x\right]\Phi=0\\
&\left[\big(\tfrac{d}{dq}\big)^2+\tfrac{3}{2}\eta^{-1} x^{-3/2}\tfrac{d}{dq}-\tfrac{1}{4}\eta^{-2}x^{-3}-1\right]\Phi=0\\
&\left[\big(\tfrac{d}{dq}\big)^2+q^{-1}\tfrac{d}{dq}-\tfrac{1}{9}q^{-2}-1\right]\Phi=0\,.
\end{split}\end{equation*}
This shows that $\Phi(q)$ satisfies the transformed Airy equation \eqref{eqn:reg-mod-bessel}.
